### 2018-01-19 Chapters/Chapter01.tex
Update on Overleaf.

Bitcoin (BTC) is the first digital currency, also known as digital money, internet money and cryptocurrency. It is the first currency based on cryptography techniques, distributed and decentralized, and with no central bank. Bitcoin is distributed since its ledger is public and is stored in thousands of computers. It is decentralized because there is no authority (or government) who decides its future --- any decision must be accepted by its community. The security of Bitcoin relies on digital signature technology, so the owner of some BTC tokens is, in fact, the owner of a pair of private and public keys. One may either use the private key to transfer some tokens to another, or use the public key to a proof-of-ownership. If one looses their private key, unfortunately, access to their coins will be lost forever.

Since 2009, Bitcoin has been growing and becoming widely used all around the world. It started as an experiment based in a seminal work from \citet{nakamoto2008bitcoin} and expanded to the most important and successful cryptocurrency with a \$36 billion market capitalization \citep{coinmarketcapbtc}. There are hundreds of companies investing in different uses of the technology, from exchanges to debit cards, and billions of dollars being invested in the new markets created by Bitcoin.

@@

Despite Bitcoin's huge success, there are still many challenges to be overcome. The network must scale to support hundreds of transactions per second, but today its capacity is close to 8 transactions per second. Another important challenge is to reduce the size of the ledger (or blockchain), which today is around 125GB and is growing at a rate of 4.5GB per month \citep{blockchaininfosize}.

@@

@@

@@

In a transaction, the inputs are pointers to other transactions' outputs (which they are spending). A transaction output may only be spent once and thus may not be partially spent. For instance, when one has 3 BTCs in one transaction output and would like to send 1 BTC to a friend, they have to create a transaction with one input spending the 3 BTCs and two outputs, one for the friend with 1 BTC and one's change with 2 BTCs. This enables $O(1)$ unspent transaction lookup.

>>>>

@@

Bitcoin (BTC) is the first digital currency, also known as digital money, internet money and cryptocurrency. It is the first currency based on cryptography techniques, distributed and decentralized, and with no central bank. Bitcoin is distributed since its ledger is public and is stored in thousands of computers. It is decentralized because there is no authority (or government) who decides its future --- any decision must be accepted by its community. The security of Bitcoin relies on digital signature technology and network agreement. While digital signature ensures ownership, i.e., the funds may only be spend by their owners, and nobody else; the network agreement both prevents double spending and ensures funds. In short, every transaction must spend only unspent funds, must have enough funds available, and must be signed by its owners, authorizing its execution. When all these requirements are met, the funds are transfered.

Since 2009, Bitcoin has been growing and becoming widely used all around the world. It started as an experiment based in a seminal work by \citet{nakamoto2008bitcoin} and expanded to the most important and successful cryptocurrency with a highly volatile \$192 billion market capitalization, as of this writing \citep{coinmarketcapbtc}. There are hundreds of companies investing in different uses of the technology, from exchanges to debit cards, and billions of dollars being invested in the new markets based on Bitcoin's technology.

Despite Bitcoin's huge success, there are still many challenges to be overcome. The network must scale to support hundreds of transactions per second, but, as we will see, today its capacity is close to 8 transactions per second. Another important challenge is to reduce the size of the ledger (or blockchain), which today is around 125GB and is growing at a rate of 4.5GB per month \citep{blockchaininfosize}.

% TODO Include incentives.

@@

% Describe the basics of SHA-256 algorithm.

@@

The digital signature scheme used by Bitcoin is based on a pair of private and public keys. The private key is used to sign the transaction, while the public key is used to check whether the signature is valid. Thus, the owner of some Bitcoin funds is, in fact, the owner of a pair of private and public keys. The private key must never be publicly published, as whoever has access to the private key is able to spend its funds. In other words, in order to protect their funds, the owners must protect the private key. If one looses their private key, unfortunately, access to their funds will be lost forever. The public key may be used to a proof-of-ownership, i.e., one may publish the public key with some message digitally signed by the private key, proving that he/she is the owner of the funds.

@@

In a transaction, the inputs are pointers to other transactions' outputs (which they are spending). A transaction output may only be spent once and thus may not be partially spent. For instance, when one has 3 BTCs in one transaction output and would like to send 1 BTC to a friend, they have to create a transaction with one input spending the 3 BTCs and two outputs, one for the friend with 1 BTC and one's change with 2 BTCs. This enables $O(1)$ unspent transaction lookup. % Improve explanation of O(1).
